### 2021-01-20 publications/2020-03-paper/cover-letter/cover_letter.tex
fixes logo issue
Former-commit-id: cd00320ab496dbea42ee18fb50a9d124186caa5e
Former-commit-id: afe3ac4ca7c6845b83e75aaacd583a6e6051f90c
signature correction
Former-commit-id: b3d6bd2e31e43a454901d072ae65a568eca85a4a
Former-commit-id: 30dac75a5b42023debe49869fffc6bd361c99cf4
adjusts table widths
Former-commit-id: 93ef12ba16bfcc32ee9d78c4b2209be9034e2c6c
Former-commit-id: 182aa7c602d60e40d5de034df1c57fceae38efe1

% Margins
\usepackage[left=1.25in,right=1.25in,top=1in,bottom=0.5in]{geometry}
%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
%\usepackage{everypage}
%\usepackage{blindtext}
%\usepackage{eso-pic,graphicx}
 \begin{document}
%\AddToShipoutPictureBG*{\includegraphics[width=\paperwidth,height=\paperheight]{background.pdf}}

@@

Please find enclosed our manuscript entitled: ``The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals for Japan'' which I and my co-authors, Chapman, Minami, Stubbins, and Huff, 
are submitting for exclusive consideration for publication as a research 
article in Progress in Nuclear Energy.

Our work uses TIMES framework to explore decarbonisation pathways for the Japanese electricity supply sector using conventional and emerging (hydrogen, carbon capture and sequestration, and emerging photovoltaic cells) technologies. This work is novel in its inclusion of nascent technologies like solid oxide electrolysers and photochemical water splitting reactors, long-term impact evaluation up to the year 2100, life-cycle emissions for all technologies, and projections and learning curves for parameters like capital costs. We assess novel technologies’ impact using a rigorous sensitivity analysis.

Our results approach true carbon-neutrality with the incorporation of lifecycle emissions. We also find that Japan can achieve energy security while mitigating emissions using renewable-based hydrogen. Further, incorporation of nuclear along with hydrogen emerges as an economically viable strategy with continued emission reduction until 2100. Our sensitivity analysis identifies key emerging technologies, and their most impactful parameters.

Our work will offer a detailed comparative assessment of transition strategies to global energy analysts and Japanese policymakers. Our sensitivity analysis will also inform near-term deployment goals of mature technologies and long-term research objectives for lab-scale technologies in Japan.

@@

\closing{Sincere regards,
%\includegraphics[height=2cm]{signature}\\
\fromsig{Anshuman Chaube\\PhD Candidate\\Nuclear, Plasma, \& Radiological 
Eng.\\University of Illinois\\achaube2@illinois.edu}
}

>>>>

% Margins
\usepackage[left=1.25in,right=1.25in,top=1in,bottom=0.5in]{geometry}
%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
%\usepackage{everypage}
%\usepackage{blindtext}
\usepackage{eso-pic}
\usepackage{graphicx}

 \begin{document}
%\ClearShipoutPicture
\AddToShipoutPictureBG*{\includegraphics[width=\paperwidth,height=\paperheight]{background.pdf}}

@@

Please find enclosed our manuscript entitled: ``The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals'' which I and my co-authors, Chapman, Minami, Stubbins, and Huff 
are submitting for exclusive consideration for publication as a research 
article in Applied Energy.

Our work uses the TIMES framework to explore decarbonisation pathways for the Japanese electricity supply sector using conventional and emerging (hydrogen, carbon capture and sequestration, and emerging photovoltaic cells) technologies. This work is novel in its inclusion of nascent technologies like solid oxide electrolysers and photochemical water splitting reactors, long-term impact evaluation up to the year 2100, life-cycle emissions for all technologies, and projections and learning curves for parameters like capital costs. We assess emerging technologies’ impact using a rigorous sensitivity analysis.

Our results approach true carbon-neutrality with the incorporation of lifecycle emissions. We also find that Japan can achieve energy security while mitigating emissions using renewable-based hydrogen. Further, incorporation of nuclear along with hydrogen emerges as an economically viable strategy. Our sensitivity analysis identifies key emerging technologies, and their most impactful parameters.

Our work offers a detailed comparative assessment of transition strategies to global energy analysts and Japanese policymakers. Our sensitivity analysis will also inform near-term deployment goals of mature technologies and long-term research objectives for lab-scale technologies in Japan.

@@

\closing{Sincere regards,\\
%\includegraphics[height=2cm]{signature}\\
\fromsig{Anshuman Chaube\\PhD Candidate\\Nuclear, Plasma, \& Radiological 
Eng.\\University of Illinois.\\achaube2@illinois.edu}
}
